A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-06 article/article.tex
work on the embeddings

>>>>

The exact architecture of the model is shown in Figure \ref{fig:model_architecture}. The features used are the actor type (as a one hot encoding),
the actor speed (float), if the actor is on an intersection (boolean) and if the actor changed its lane since the last timestep (boolean) for the nodes.
For the edges, the edge type (as a one hot encoding) and the path length (float) between the two nodes are used.
